### 2017-11-04 monograph/thesis/chapters/beautifiers.tex
Improved the beautifiers.tex For what is their use?' section
introduction.

    For now could not find any strong evidence or correlation about code
    comprehension and source code beautifying .

@@

>>>>

    For now could not find any strong evidence or correlation about code
    comprehension and source code beautifying \cite{improvingCodeReadability},
    except perhaps for team annoyance:

@@

    On \citeonline{improvingCodeReadability} was analyzed the level of program
    comprehension which can be gained by the indentation and was constated that
    the indentation levels of 2 and 4 spaces proved to have the best
    comprehension levels again other levels.

### 2017-11-04 monograph/thesis/chapters/introduction.tex
Improved the beautifiers.tex For what is their use?' section
introduction.

    In this proposal last chapter which lies on the part
    called `\nameref{sec:implementation}', which holds the implementation of a
    tool for code `Beautifying'.

>>>>

    In this proposal last chapter which lies on the part
    called `\nameref{sec:software_implementation}', which holds the implementation of a
    tool for code `Beautifying'.
